{\sc Kalashnikov}: Fully Automatic Loop Free Program Synthesis by Bounded Model Checking

### 2013-09-26 paper/paper.tex
Added flow chart to paper

Unfortunately we saw quite the opposite effect -- runtimes when implementing the
$\mathcal{L}$-interpreter as a stack machine were much higher than the three-address
code implementation.  We believe the reason for this
effect is that the internal state of a stack based interpreter is much more complex
to analyse than an interpreter for three-address code.  This is because a
three-address code interpreter can be implemented using a single array whose cells are
each written to exactly once (each cell corresponds to a register in the program).
By contrast a stack machine interpreter has a stack as its central data structure.
It is natural to implement this as an array, but the array's contents are accessed
in an unpredictable, non-uniform manner as the stack pointer increases and decreases
over the lifetime of the program.  This leads to a \emph{larger} SAT
isntance and drastically slows down the operation of the solver.

>>>>

Unfortunately we saw quite the opposite effect -- runtimes when implementing the
$\mathcal{L}$-interpreter as a stack machine were much higher than the three-address
code implementation.  We believe the reason for this
effect is that the internal state of a stack based interpreter is much more complex
to analyse than an interpreter for three-address code.  This is because a
three-address code interpreter can be implemented using a single array whose cells are
each written to exactly once (each cell corresponds to a register in the program).
By contrast a stack machine interpreter has a stack as its central data structure.
It is natural to implement this as an array, but the array's contents are accessed
in an unpredictable, non-uniform manner as the stack pointer increases and decreases
over the lifetime of the program.  This leads to a \emph{larger} SAT
instance and drastically slows down the operation of the solver.

\begin{figure}
\begin{tikzpicture}{node distance=2cm, auto}
\tikzstyle{decision} = [diamond, draw, fill=blue!20, 
    text width=4.5em, text badly centered, node distance=3cm, inner sep=0pt]
\tikzstyle{block} = [rectangle, draw, fill=blue!20, 
    text width=5em, text centered, rounded corners, minimum height=4em]
\tikzstyle{line} = [draw, -latex']
\tikzstyle{cloud} = [draw, ellipse,fill=red!20, node distance=3cm,
    minimum height=2em]

 \node [decision] (synthsucc) {{\sc Synth} succeeds?};

 \node [decision, below of=synthsucc, node distance=2.5cm] (verif) {{\sc Verif} succeeds?};
 \node [decision, right of=verif] (ck) {$c < k$?};

 \node [block, below of=verif, node distance=2.5cm]   (done) {Done!};
 \node [decision, left of=done] (verifw) {{\sc Verif} succeeds for small words?};

 \node [block, below of=ck, node distance=2.5cm] (incc) {$c := c+1$};
 \node [block, right of=incc, node distance=2cm] (inck) {$c := 0$\\ $k := k+1$};

 \node [block, below of=verifw, node distance=2.5cm] (incw) {$w := w+1$};
 \node [block, left of=incw, node distance=2cm] (iterate) {Loop to {\sc synth}};

 \path [line] (synthsucc) -- node [left] {Yes} (verif);
 \path [line] (synthsucc) -| node [above, near start] {No} (ck);

 \path [line] (verif) -- node [left] {Yes} (done);
 \path [line] (verif) -| node [above, near start] {No} (verifw);

 \path [line] (ck) -- node [left] {Yes} (incc);
 \path [line] (ck) -| node  [above, near start]  {No}(inck);

 \path [line] (verifw) -- node [right] {Yes} (incw);
 \path [line] (verifw) -| node [above, near start] {No} (iterate);
\end{tikzpicture}

\label{fig:paramsflow}
 \caption{Decision tree for increasing parameters of $\mathcal{L}$.}
\end{figure}
